\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Date1 & Name(s) & Description of changes\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

\wss{Put your introductory blurb here.  Often the blurb is a brief roadmap of
what is contained in the report.}

\wss{Additional information on the development plan can be found in the
\href{https://gitlab.cas.mcmaster.ca/courses/capstone/-/blob/main/Lectures/L02b_POCAndDevPlan/POCAndDevPlan.pdf?ref_type=heads}
{lecture slides}.}

\section{Confidential Information?}

This project does not contain any confidental information from industry partners.

\section{IP to Protect} 

This project does not require any IP

\section{Copyright License}

\wss{What copyright license is your team adopting.  Point to the license in your
repo.}
See LICENSE file in root of repository. It can be accessed at this
\href{https://github.com/hitchly/hitchly/blob/main/LICENSE}{link}.

\section{Team Meeting Plan}

\wss{How often will you meet? where?}

\wss{If the meeting is a physical location (not virtual), out of an abundance of
caution for safety reasons you shouldn't put the location online}

\wss{How often will you meet with your industry advisor?  when?  where?}

\wss{Will meetings be virtual?  At least some meetings should likely be
in-person.}

\wss{How will the meetings be structured?  There should be a chair for all meetings.  There should be an agenda for all meetings.}

\section{Team Communication Plan}

Our team will use several platforms for communication to stay as organized and connected as possible.
\begin{itemize}
	\item {\bf Github:} This will be the central platform for code collaboration and project task management. 
	\begin{itemize}
    \item The team will use Issues to log tasks and meetings, and to assign responsibilities.
    \item Project boards will be used to help track the team's progress throughout the project.
  \end{itemize}
  \item {\bf Discord:} This will be used as the primary communication platform for the team. 
        Meetings will take place in the Discord server, as well as any other quick communication, updates, and questions.
  \item {\bf Microsoft Teams:} Teams will also be used to share files and documents to stay organized.
  \item {\bf Outlook:} Email will be used to communicate with the Professor, TA, and any other external inquiries related to the project.
\end{itemize}

\section{Team Member Roles}

The roles outlined below will guide the workflow of the team and ensure key responsibilities are covered, but remain flexible to allow all members to rotate respinsibilities
and step in for each other as we progress through the project, allowing each member to get experience in a number of areas. While all members of the team
will be required to contribute to development, doocumentation, and other general tasks of the project, certain criticial aspects of the project that require 
domain expertise and consistent oversight will have designated leads. The leads ensure that these areas are managed properly and provides direction and accountability for all team members.
This approach to team member roles helps balance shared learning with the need for leadership.
\begin{itemize}
  \item {\bf Meeting Chair:} This person will be responsible for taking lead of any group meetings by setting an agenda and ensuring
        everybody is on the same page by taking notes of what was discussed. They will also be responsible for taking notes during TA meetings
        and coordinating any other meetings that need to take place.
  \item {\bf Reviewer:} Reviews any pull requests and commits for documentation to ensure that the content aligns with the rest of the group's work, 
        and also fits the Exceeds criteria on the rubric. Feedback will be provided as appropriate to improve the quality of work submitted.
  \item {\bf Testing lead:} In charge of overseeing the creation and execution of test plans, which can include unit testing, integration testing, and user acceptance testing, to ensure features meet the requirements and functionality is stable. 
  \item {\bf UI/UX Lead:} Specializes in understanding user needs and designing and refining the interface of the application. Conducts usability tests
        and gathers feedback to ensure the design is user-friendly. 
  \item {\bf Data Management and Insights Lead:} Responsible for overseeing how data which is required for the application is being stored and managed
        in the app's database and schemas, and how it is integrated into the application. Also responsible for tracking key metrics such as the number of rides,
        estimated carbon footprint reduction, etc.
\end{itemize} 

\section{Workflow Plan}

{\bf Git:} The main branch in the repository is where code and documentation that has been reviewed and approved will be stored. Team members will create branches for any given task while working
on a deliverable to keep work organized and separated.  The branches that are created will have a descriptive name that mentions the task for clarity. Once the changes have been made on a branch, 
a pull request will be made explaning the changes, and the change must be reviewed by the team member who is the Reviewer at the time at the bare minimum. Once reviewed, if it is approved then the changes will be merged into the main branch. \\

\noindent {\bf Issues:} For each deliverable, the team will break it down into individual tasks, which will then have a corresponding issue created for them on Github, which will be assigned to the team member who will complete the task.
Each issue will be given a label based on what it is for (e.g: documentation), and a Type label to further clarify its purpose (e.g: Task, Bug, Feature). 
The issue will also be given a descriptive title which clearly shows what task it is related to. When a team member completes the work for a given task, their work will
be committed on Git and will be linked to the corresponding issue. Each issue will be added to a Board on git to keep track of progress. Issues will also be created to keep track of team meetings and lectures. \\

\noindent {\bf CI/CD:} We will use Github Actions to set up a CI/CD pipeline for our project. This helps ensire that every team member's code integrates smoothly. Actions that will be included will be
automated generation of documentation from the source code, running unit tests, and code style checks. These must pass in order for a Pull Request to be merged.
\section{Project Decomposition and Scheduling}

The team will be using Github projects as a central tool for organizing tasks, tracking progress, and scheduling work throughout the capstone project. As mentioned in Section 7,
the team will use issues for each task of the project, whether it be a section of documentation, delivering a feature, or a bug fix. These issues will be grouped by the milestone it
is a part of, and will be organized into columns that represent the status of the task: To do, In Progress, or Done. The team member that is assigned the task/issue is responsible
for updating the status of their task as it is worked on.\newline

\noindent The Github Project can be accessed \href{https://github.com/orgs/hitchly/projects/2/views/1}{\bf here}.\\

\noindent {\bf The project will be scheduled as follows:}

\begin{table}[h!]
  \centering
  \begin{tabular}{|l|l|}
  \hline
  \textbf{Task/Deliverable} & \textbf{Deadline} \\
  \hline
  Problem Statement, POC Plan, Development Plan & Sept 22, 2025 \\
  \hline
  Requirements Document and Hazard Analysis Revision 0 & Oct 6, 2025 \\
  \hline
  V\&V Plan Revision 0  & Oct 27, 2025 \\
  \hline
  Design Document Revision -1  & Nov 10, 2025 \\
  \hline
  Proof of Concept Demonstration & Nov 17-27, 2025 \\
  \hline
  Design Document Revision 0           & Jan 19, 2026 \\
  \hline
  Revision 0 Demonstration & Feb 2-12, 2026 \\
  \hline
  V\&V Report and Extras Revision 0 & Mar 9, 2026 \\
  \hline
  Final Demonstration (Revision 1) & Mar 23-29, 2026 \\
  \hline
  EXPO Demonstration & TBD \\
  \hline
  Final Documentation (Revision 1) & Apr 6, 2026 \\
  \hline
  \end{tabular}
  \caption{Project Schedule with Deadlines}
  \label{tab:schedule}
  \end{table}

\section{Proof of Concept Demonstration Plan}

% What is the main risk, or risks, for the success of your project?  What will you
% demonstrate during your proof of concept demonstration to convince yourself that
% you will be able to overcome this risk?

The primary risks for this project are user trust and safety and the reliability of the ride-matching system.
Without a secure verification process tied to McMaster email accounts, users may hesitate to adopt the platform.
Similarly, if the matching algorithm fails to correctly pair riders and drivers based on schedules and locations, the application will not provide value.
The proof of concept will focus on validating these two core capabilities:

\begin{itemize}
  \item \textbf{McMaster Email Verification}
  \begin{itemize}
      \item Users must sign up using a McMaster-affiliated email.
      \item Verification ensures that only students, staff, and faculty can access the platform.
      \item Demonstrates credibility and mitigates safety concerns for early users.
  \end{itemize}

  \item \textbf{Ride Matching Prototype}
  \begin{itemize}
      \item A minimal matching engine takes sample schedules and trip data from riders and drivers.
      \item Produces correct pairings with cost-sharing estimates.
      \item Confirms feasibility of integrating timetable and location-based logic.
  \end{itemize}
\end{itemize}

By validating these areas first, the team ensures the platform addresses its two biggest risks of safety and usability before expanding into additional features such as live tracking, queuing, or ratings.


\section{Expected Technology}

% \wss{What programming language or languages do you expect to use?  What external
% libraries?  What frameworks?  What technologies.  Are there major components of
% the implementation that you expect you will implement, despite the existence of
% libraries that provide the required functionality.  For projects with machine
% learning, will you use pre-trained models, or be training your own model?  }

% \wss{The implementation decisions can, and likely will, change over the course
% of the project.  The initial documentation should be written in an abstract way;
% it should be agnostic of the implementation choices, unless the implementation
% choices are project constraints.  However, recording our initial thoughts on
% implementation helps understand the challenge level and feasibility of a
% project.  It may also help with early identification of areas where project
% members will need to augment their training.}

% Topics to discuss include the following:

% \begin{itemize}
% \item Specific programming language
% \item Specific libraries
% \item Pre-trained models
% \item Specific linter tool (if appropriate)
% \item Specific unit testing framework
% \item Investigation of code coverage measuring tools
% \item Specific plans for Continuous Integration (CI), or an explanation that CI
%   is not being done
% \item Specific performance measuring tools (like Valgrind), if
%   appropriate
% \item Tools you will likely be using?
% \end{itemize}

% \wss{git, GitHub and GitHub projects should be part of your technology.}

The project will be built as a \textbf{cross-platform mobile application} for iOS and Android. The technology stack covers the full lifecycle: ideation, design, development, testing, deployment, and app store release.

\subsection*{a. Concept Ideation \& Design}
\begin{itemize}
    \item \textbf{Wireframing \& Prototyping:} Figma for user flows, wireframes, and visual design.
    \item \textbf{Collaboration \& Task Management:} GitHub Projects for task tracking, milestones, and agile planning.
\end{itemize}

\subsection*{b. Frontend (Mobile App)}
\begin{itemize}
    \item \textbf{Framework:} React Native with Expo (cross-platform).
    \item \textbf{Language:} TypeScript for static typing and type safety.
    \item \textbf{UI \& Styling:} Tailwind CSS via NativeWind and shadcn/ui for consistent styling.
    \item \textbf{Navigation:} React Navigation for multi-screen flows.
    \item \textbf{State Management \& Data Fetching:} React Query integrated with tRPC client for type-safe server communication.
\end{itemize}

\subsection*{c. Backend \& API}
\begin{itemize}
    \item \textbf{Framework:} tRPC running on Node.js (standalone server serving the mobile app).
    \item \textbf{Language:} TypeScript (shared between frontend and backend).
    \item \textbf{Hosting:} Railway for backend server and PostgreSQL database (low cost, minimal maintenance).
    \item \textbf{Authentication:} 
    \begin{itemize}
        \item McMaster email domain verification at signup.
        \item JWT for secure session handling.
    \end{itemize}
    \item \textbf{Core Services:} Matching engine, ride scheduling, and trip storage.
\end{itemize}

\subsection*{d. Database \& Persistence}
\begin{itemize}
    \item \textbf{Database:} PostgreSQL for structured relational data.
    \item \textbf{ORM:} Drizzle ORM for schema management and migrations.
    \item \textbf{Hosting:} Managed PostgreSQL via Railway.
\end{itemize}

\subsection*{e. Testing \& Quality Assurance}
\begin{itemize}
    \item \textbf{Unit Testing:} Jest for frontend and backend logic.
    \item \textbf{Integration Testing:} Supertest for backend endpoint verification.
    \item \textbf{Static Analysis:} ESLint and Prettier for linting and formatting.
\end{itemize}

\subsection*{f. Development Workflow \& CI/CD}
\begin{itemize}
    \item \textbf{Version Control:} Git + GitHub repository.
    \item \textbf{Branching Strategy:} Feature branches with pull requests.
    \item \textbf{CI/CD:} GitHub Actions for automated testing, linting, type-checking, and deployments.
    \item \textbf{Environments:}
    \begin{itemize}
        \item Development: Local Expo Go + Railway database.
        \item Staging: Railway preview deployment + Expo EAS preview builds.
        \item Production: Stable backend deployments + app store builds.
    \end{itemize}
\end{itemize}

\subsection*{g. Deployment \& Hosting}
\begin{itemize}
    \item \textbf{Backend Deployment:} Railway containerized Node.js hosting.
    \item \textbf{Database Deployment:} Railway managed PostgreSQL.
    \item \textbf{Frontend Builds:} Expo EAS Build for iOS and Android binaries.
    \item \textbf{App Store Distribution:}
    \begin{itemize}
        \item Apple App Store via Expo EAS.
        \item Google Play Store via Expo EAS.
    \end{itemize}
\end{itemize}


\section{Coding Standard}

% \wss{What coding standard will you adopt?}

To maintain \textbf{clarity, maintainability, and collaboration}, the team will adopt the following coding standards:

\subsection*{Style \& Formatting}
\begin{itemize}
    \item TypeScript with consistent naming conventions and modular architecture.
    \item ESLint and Prettier enforce linting and formatting across the codebase.
\end{itemize}

\subsection*{Documentation}
\begin{itemize}
    \item JSDoc comments for functions, APIs, and modules.
    \item Inline comments for complex logic (e.g., ride-matching algorithm).
\end{itemize}

\subsection*{Version Control Practices}
\begin{itemize}
    \item Git with feature branches for all new work.
    \item Pull requests with mandatory peer review before merging.
    \item All commits to main branch must be squashed and merged (enforced via GitHub rulesets).
    \item Descriptive commit messages using Conventional Commits format.
    \item GitHub Projects for issue tracking, milestones, and labeling (bug, feature, documentation, etc.).
\end{itemize}

\subsection*{Testing Practices}
\begin{itemize}
    \item Unit tests for core features (authentication, ride matching).
    \item Integration tests for backend endpoints.
\end{itemize}

These standards ensure the codebase is \textbf{professional, maintainable, and scalable}, meeting rubric expectations for a senior design project.

\newpage{}

\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\begin{enumerate}
  \item \textbf{Why is it important to create a development plan prior to starting the project?} \\ 
  Creating a development plan is important because it establishes structure, expectations, and direction for the team before work begins. It ensures that roles, responsibilities, communication methods, and goals are clearly defined, which reduces confusion later in the project. It also helps identify risks early and provides a roadmap that keeps the team accountable and aligned.
  \item \textbf{In your opinion, what are the advantages and disadvantages of using CI/CD?} \\ 
  The main advantages of CI/CD are faster development cycles, early detection of bugs, and consistent integration of code, which reduces the likelihood of major conflicts at later stages. It also enforces good coding practices and increases overall software reliability. However, disadvantages include the setup time and learning curve required, especially for a student project, as well as the overhead of maintaining pipelines and infrastructure when the team may already be managing heavy coursework.
  \item \textbf{What disagreements did your group have in this deliverable, if any, and how did you resolve them?} \\ 
  Not in this deliverable in particular, but earlier we had a disagreement regarding the proposal idea for our capstone project. After debating with facts and reasoning, we collectively concluded that pursuing the rideshare project would be the most impactful and feasible direction for our team.
\end{enumerate}

\newpage{}

\section*{Appendix --- Team Charter}

\subsection*{External Goals}

Our external goals for this project are to develop an application that delivers meaningful real-world impact that also extends beyond the scope of capstone. We aim to achieve a high grade in this course, higher than a 10, while also competing at the Capstone EXPO and presenting our work to the McMaster community. In addition, we intend for this project to serve as a strong portfolio piece, highlighting our technical, design, and collaborative skills to future employers. Finally, we recognize the potential for this project to evolve into a startup, enabling it to create value and impact beyond the university setting—potentially the next big ride app competing against Uber and Lyft.

\subsection*{Attendance}

\subsubsection*{Expectations}

Our team expects all members to treat meetings as a priority and respect one another’s time by being punctual and engaged. Attendance is essential to keep the project on track, and clear communication is expected whenever conflicts arise.

\begin{itemize}
    \item Members should arrive on time; being more than 10 minutes late without notice is discouraged, as it is disruptive and shows a lack of respect for everyone else’s time.
    \item No more than 2 unexcused absences are permitted per term.
    \item Leaving early or joining late is only acceptable if communicated beforehand.
    \item Members are expected to be fully present during meetings and avoid unrelated activities.
    \item Anyone who misses a meeting is responsible for reviewing notes and following up to stay up to date.
\end{itemize}

\subsubsection*{Acceptable Excuse}

\begin{itemize}
    \item Transit delays, weather issues, or unforeseen personal emergencies (as long as the team is notified).
    \item Illness, family emergencies, or direct academic conflicts such as exams or required presentations.
    \item Overlapping academic or work responsibilities, or unavoidable scheduling conflicts that are shared in advance.
    \item Urgent situations (e.g., emergency calls or messages) that require brief attention, but members should minimize distractions.
\end{itemize}

\textbf{Note:} There is no acceptable excuse for failing to review notes and catch up after missing a meeting — this is always the member’s responsibility.

\subsubsection*{In Case of Emergency}

If a team member experiences an emergency and cannot attend a meeting or complete their assigned work:
\begin{itemize}
    \item They must notify the team as soon as possible through the primary communication channel (e.g., Discord/Teams).
    \item No personal details need to be shared beyond confirming that it is an emergency.
    \item The member should communicate how much of their work has been completed and what remains outstanding.
    \item If the task cannot be finished in time, the member should either:
    \begin{itemize}
        \item Delay completion and commit to catching up later, or
        \item Transfer responsibility to another team member, providing enough context or materials to allow for a smooth handoff.
    \end{itemize}
    \item If responsibility is transferred, the original member should agree on how they will make up their contribution in a future task to keep workloads fair.
\end{itemize}


\subsection*{Accountability and Teamwork}

\subsubsection*{Quality}

Our team expects all members to come prepared for meetings, with assigned tasks completed to a high standard. Deliverables should be accurate, polished, and ready for integration or review. Members are encouraged to review one another’s work to ensure consistency and to help catch errors early. The expectation is to go beyond simply completing tasks, aiming instead to produce work that reflects professionalism and attention to detail.

\subsubsection*{Attitude}

Team members are expected to maintain a positive and professional attitude, respecting all contributions and encouraging open discussion. All ideas will be heard and considered, but discussion should remain solutions focused. Disagreements will be handled constructively, using a clear process: clarify the issue, listen to all perspectives, establish common ground, and agree on a resolution.

\subsubsection*{Stay on Track}

Our team will stay accountable by setting measurable targets and monitoring progress regularly. Each member is expected to contribute fairly and consistently so that the workload is balanced, and deadlines are met.

\vspace{0.5em}
\noindent\textbf{Metrics:}
\begin{itemize}
    \item \textbf{Attendance:} Members are expected to attend at least 90\% of scheduled meetings.
    \item \textbf{Commits:} Each member should make regular commits (minimum 2 per week), reflecting steady progress.
    \item \textbf{Issues:} All members must contribute to opening, discussing, and closing GitHub Issues, with at least 1--2 issues closed per week per person.
    \item \textbf{Documentation \& Reviews:} Members are expected to contribute to documentation and review teammates’ work at least once per deliverable.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Rewards:}
\begin{itemize}
    \item The top contributor for each milestone (measured by commits, issues closed, and meeting contributions) will be recognized and treated to a free lunch by the team.
    \item Members who consistently meet or exceed expectations may receive lighter workloads during peak deadlines as recognition.
\end{itemize}

\vspace{0.5em}
\noindent\textbf{Consequences:}
\begin{itemize}
    \item Members falling short of expectations will first receive a reminder and the chance to catch up.
    \item If underperformance persists, the issue will be discussed with the TA or instructor and reflected in peer evaluations.
    \item For minor misses (e.g., attendance or commits), fun consequences may be applied, such as bringing coffee/snacks to the next meeting.
\end{itemize}
\subsubsection*{Team Building}

Cohesion will be maintained through open communication, supportive collaboration, and celebrating milestones together. Occasional informal check-ins will help strengthen relationships and ensure a positive team culture.

\subsubsection*{Decision Making}

Decisions will aim for consensus whenever possible. If consensus cannot be reached, the team will rely on rational, objective, and fact-based decision making rather than subjective opinions. Evidence, data, and alignment with project goals will guide choices. As a last resort, majority voting will be used.

\end{document}