\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}
    
\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Hamzah Rawasia & 3\\
Sarim Zia & 2\\
Aidan Froggatt & 3\\
Swesan Pathmanathan & 3\\
Burhanuddin Kharodawala & 3\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{McMaster Students/Staff}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Hamzah Rawasia & 2\\
Sarim Zia & 2\\
Aidan Froggatt & 2\\
Swesan Pathmanathan & 2\\
Burhanuddin Kharodawala & 2\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 0\\
Hamzah Rawasia & 0\\
Sarim Zia & 0\\
Aidan Froggatt & 0\\
Swesan Pathmanathan & 0\\
Burhanuddin Kharodawala & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: Lucas Dutton} [fill in this information]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Hamzah Rawasia & 1\\
Sarim Zia & 1\\
Aidan Froggatt & 1\\
Swesan Pathmanathan & 1\\
Burhanuddin Kharodawala & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 69 & 100\% \\
Hamzah Rawasia & 18 & 26.09\% \\
Sarim Zia & 7 & 10.14\% \\
Aidan Froggatt & 20 & 28.99\% \\
Swesan Pathmanathan & 15 & 21.74\% \\
Burhanuddin Kharodawala & 9 & 13.04\% \\
\bottomrule
\end{tabular}
\end{table}

Sarim and Burhanuddin's contributions were more focused on documentation and testing, which may not be fully reflected in the commit count.

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Hamzah Rawasia & 3 & 1 \\
Sarim Zia & 1 & 0 \\
Aidan Froggatt & 2 & 1 \\
Swesan Pathmanathan & 1 & 0 \\
Burhanuddin Kharodawala & 2 & 0 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}
The team's quantified triggers were established to maintain accountability and consistent progress throughout the project lifecycle.
 These triggers included a limit of no more than two unexcused absences per term, a requirement for each member to maintain regular
  commit history and active participation in issue management, and a mandatory peer-review process for all work prior to final submission. 

To date, there have been no documented violations of these triggers; in instances where a team member could not attend a meeting or fulfill 
a specific rule, they proactively informed the group with a valid justification, ensuring continuous alignment. However, as the project entered its
 final stages, the team identified that the ``regular commit'' trigger was structurally weak and ambiguous. It incorrectly assumed that project distribution
  was measured solely through code contributions, failing to account for critical non-technical deliverables such as the project poster and the final presentation slideshow. 

To address this, the team held a meeting to revise the trigger to encompass regular contributions to all project facets. This updated metric now explicitly includes commits,
 documentation, and presentation materials. The team will continue to monitor these contributions through the final stretch of the capstone to ensure equitable workload distribution
  and make further adjustments as necessary.
\section{Additional Productivity Metrics}
N/A

\end{document}