\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

Our focus will be on the algorithm for the rideshares application, as well as McMaster email authentication. We will complete the workflow by verifying your McMaster email, creating a sufficient algorithm including certain parameters such as user schedule, location, and time. The users will be able to connect and complete a simple rideshare between a driver and one passenger. Both users will then receive the ride summary including a cost breakdown. 


\section{Team Meeting Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 10\\
Hamzah Rawasia & 9\\
Aidan Froggatt & 8\\
Burhanuddin Kharodawala & 10\\
Sarim Zia & 8\\
Swesan Pathmanathan & 10\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } N/A

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 0\\
Hamzah Rawasia  & 0\\
Sarim Zia & 0\\
Aidan Froggatt & 0\\
Swesan Pathmanathan & 0\\
Burhanuddin Kharodawala & 0\\
\bottomrule
\end{tabular}
\end{table}\\

\noindent We don't have a supervisor for the project and we have not conducted any meeting with our stakeholders currently.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 12\\
Hamzah Rawasia & 10\\
Aidan Froggatt & 9\\
Burhanuddin Kharodawala & 6\\
Sarim Zia & 8\\
Swesan Pathmanathan & 8\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } Lucas Dutton

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{TA Meetings}\\
\midrule
Total & 5\\
Hamzah Rawasia  & 5\\
Sarim Zia & 5\\
Aidan Froggatt & 4\\
Swesan Pathmanathan & 5\\
Burhanuddin Kharodawala & 4\\
\bottomrule
\end{tabular}
\end{table} \\

\noindent Members who missed any meetings had a valid reason which was shared with the team beforehand.


\section{Commits}


\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 129 & 100\% \\
Hamzah Rawasia & 27 & 20.9\% \\
Aidan Froggatt & 27 & 20.9\% \\
Burhanuddin Kharodawala & 33 & 28.7\% \\
Sarim Zia & 32 & 24.8\% \\
Swesan Pathmanathan & 6 & 4.8\% \\
\bottomrule
\end{tabular}
\end{table}

We have many coauthored commits, also the commits are greatly varying in amount of content and time per contribution. Commits have been merged into main in a variety of differing formats which results in a smaller or greater number of commits than amount of content. 

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Hamzah Rawasia & 19 & 13 \\
Aidan Froggatt & 22 & 22 \\
Burhanuddin Kharodawala & 14 & 14 \\
Sarim Zia & 13 & 13 \\
Swesan Pathmanathan & 10 & 10 \\
\bottomrule
\end{tabular}
\end{table}


\section{CICD}

Hitchly employs a Continuous Integration and Continuous Deployment (CI/CD) pipeline using 
GitHub Actions and Docker to ensure consistent quality, reliability, and maintainability 
across all project components.

\subsection{Continuous Integration}

Every pull request triggers automated workflows that:
\begin{itemize}
  \item Install dependencies via \texttt{pnpm} within the Turborepo monorepo.
  \item Run ESLint, Prettier, and TypeScript checks for code quality and type safety.
  \item Execute unit tests (Jest) and verify build integrity for the API and mobile app.
\end{itemize}
This guarantees that only validated, production-ready code is merged into the main branch.

\subsection{Continuous Deployment}

Successful merges to \texttt{main} trigger Docker-based deployments of the Express/tRPC API 
to the cloud environment and Expo EAS builds for the mobile client. Drizzle ORM migrations 
are automatically applied to synchronize the database schema with production.


\section{Team Charter Trigger Items}

Triggers included no more than 2 unexcused absences per term, each member should make regular commits and contribute to opening and closing issues, and review teammates work before submission. So far, we have not had any violations of triggers, as any members that were unable to attend a meeting or any other discussed rule informed the team ahead of time with a valid reason. Throughout the project, we will continue to assess the triggers we set in the team charter and modify them as appropriate when we find that they can be further improved and realistic for all members.  

\section{Additional Productivity Metrics}

N/A

\end{document}