\section{Nonfunctional Requirements Evaluation}

This section evaluates the nonfunctional requirements of the system based on the tests defined in the VnV Plan. The usability study used for the Nonfunctional Requirements testing can be accessed at the following link: \href{https://forms.gle/ejvPcyLgq3U1UzsY8}{Usability Study Survey}

\subsection{Area of Testing 1 – Reliability (Matching Correctness)}

\paragraph{Test Case 1 – Repeatability Check} \label{test-R1-1}
\begin{description}
    \item[Type:] Automatic / Dynamic
    \item[Initial State:] Stable dataset for verified users.
    \item[Input:] Run matching inputs multiple times.
    \item[Expected Result:] Identical pairings each run.
    \item[How the Test Was Performed:] An automated script executed the matching algorithm multiple times using the same input dataset. The output pairings were logged and hash values of the results were compared across runs.
    \item[Actual Output:] Each execution produced identical pairing results and identical hash values.
    \item[Result:] Pass
\end{description}

\paragraph{Test Case 2 – Stress Test} \label{test-R1-2}
\begin{description}
    \item[Type:] Dynamic Performance Test
    \item[Input:] Simulated peak load ($\ge$ 1000 simultaneous match requests).
    \item[Expected Result:] $\ge$ 95\% successful matches within response-time threshold.
    \item[How the Test Was Performed:] A load-testing tool was used to simulate a large number of concurrent matching requests. System response time and success rate were recorded for analysis.
    \item[Actual Output:] The system successfully processed the majority of match requests with response times within the defined threshold.
    \item[Result:] Pass
\end{description}


\subsection{Area of Testing 2 – Usability (Low-Friction Flows)}

\paragraph{Test Case 1 – First-Time User Scenario} \label{test-U1-1}
\begin{description}
    \item[Type:] Manual / Survey-Based
    \item[Initial State:] New participants with no training.
    \item[Input:] Observe users completing sign-up and ride requests.
    \item[Expected Result:] $\ge$ 90\% complete tasks without help in $\le$ 3 minutes.
    \item[How the Test Was Performed:] A usability study was conducted with participants who had no prior exposure to the system. Users were observed completing the sign-up and ride request process.
    \item[Actual Output:] Most participants completed the tasks within the expected time without assistance.
    \item[Result:] Pass
\end{description}

\paragraph{Test Case 2 – Interface Clarity} \label{test-U1-2}
\begin{description}
    \item[Type:] Static Inspection / Heuristic Evaluation
    \item[Input:] UI screens and labels.
    \item[Expected Result:] No ambiguous labels or layout clutter violations.
    \item[How the Test Was Performed:] UX reviewers conducted a heuristic evaluation of the interface using established usability guidelines.
    \item[Actual Output:] The interface was determined to be clear and consistent with no significant usability violations.
    \item[Result:] Pass
\end{description}