\section{Comparison to Existing Implementation}

To better understand the effectiveness of the proposed system,
Hitchly, it is useful to compare it with existing ride-sharing
platforms such as Uber, Lyft, and Poparide. These systems provide
transportation services using mobile applications and large driver
networks, ranging from carpooling to on-demand rides. While the core
concept of connecting riders and drivers is similar, the goals and
design of Hitchly differ in several important ways.

\subsection{Target Users}

Uber, Lyft, and Poparide are designed for the general public and
operate on a global scale. Hitchly is specifically designed for
university students and faculty at McMaster University, focusing on
a smaller, community-based user group. Restricting the system to
verified McMaster University users increases trust between riders
and drivers.

\subsection{Matching Model}

Uber, Lyft, and Poparide share a similarity in that they do not
emphasize driver–rider interaction beyond the ride itself. Hitchly
not only connects riders and drivers but also allows users to specify
preferences related to personality or behavior. Uber and Lyft also
differ from Hitchly because they use real-time driver dispatch
systems where riders are matched with the nearest available driver.
Poparide and Hitchly share a similar approach in that users have the
ability to offer or request rides that align with planned trips.

\subsection{Cost Structure}

Commercial ride-sharing platforms primarily focus on generating
profit for drivers and the platform itself. In contrast, Hitchly is
intended to reduce transportation costs for students through ride
sharing and cost splitting.

\subsection{Summary}

While Uber and Lyft provide large-scale on-demand transportation
services, Hitchly focuses on community-based ride coordination for
students. By emphasizing route matching, scheduled trips, and cost
sharing, the system provides a solution better suited for university
commuting needs.
