\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item \textbf{What went well while writing this deliverable?} 
  The structure of the VnV report benefited greatly from the organized foundation laid in the initial VnV Plan. Linking our final system tests directly to the functional and non-functional requirements (such as User Verification and Ride Matching) provided a clear roadmap for documentation. Using automated tools like Vitest and GitHub Actions also integrated naturally into our workflow, allowing for efficient coverage reporting and a cohesive final document.

  \item \textbf{What pain points did you experience during this deliverable, and how did you resolve them?}
  The most significant pain point was addressing the technical debt accumulated leading up to the Revision 0 demo. This debt made it difficult to verify certain non-functional requirements, as the code was not yet extensible enough for isolated testing. We resolved this by prioritizing a dedicated refactoring sprint focused on code quality and concern separation, which ultimately made the final verification process much smoother and improved the reliability of our test suite.

  \item \textbf{Which parts of this document stemmed from speaking to your client(s) or a proxy (e.g. your peers)? Which ones were not, and why?}
  Our primary clients are McMaster students, and their needs shaped functional requirements such as campus-specific drop-off points. Feedback from our TA and instructor served as proxies for these clients, directly leading to the refinement of drop-off location granularity and the simplified authentication flow. Conversely, the structural refactoring and UI/UX consistency improvements were developer-led initiatives. These were not driven by direct client requests but were necessary to improve the application’s professional feel and long-term maintainability.

  \item \textbf{In what ways was the Verification and Validation (VnV) Plan different from the activities that were actually conducted for VnV?}
  Several adjustments were made to the VnV activities due to resource constraints and evolving priorities:
  \begin{itemize}
      \item \textbf{Stress Testing:} While we initially planned for large-scale concurrent testing involving over 1,000 simultaneous requests, this was not completed due to limited time and testing resources. We instead focused on the correctness of the matching algorithm itself.
      \item \textbf{Usability Metrics:} Our plan originally suggested quantitative metrics like time-to-complete tasks. However, we pivoted to a best-practices approach, focusing on navigation streamlining and styling consistency based on developer audits.
      \item \textbf{Future Feature Implementation:} Features such as live location and enhanced notifications, which were highlighted during Rev 0 feedback, have been documented as part of our future development plan. We intend to incorporate these as additional technical demonstrations before the final demo rather than including them in the formal verification scope of this report.
  \end{itemize}
\end{enumerate}