\section{Module Hierarchy} \label{SecMH}

This section provides an overview of the modular design for Hitchly.  
The hierarchy follows the principle of information hiding, where each module  
encapsulates a design decision that may change independently.  
Only the leaf modules shown in Table~\ref{TblMH} are implemented.

\begin{description}

\item[\textbf{5.1 Hardware-Hiding Modules}]  
There are no hardware-hiding modules in this design.  
Hitchly relies on high-level framework APIs (Expo, React Native),  
so no direct hardware abstraction is required.

\item[\textbf{5.2 Behaviour-Hiding Modules}]  
These modules implement the user-visible behaviour of the application.  
They hide workflow logic, API interactions, and data handling that support  
Hitchly’s core features.

\begin{itemize}
  \item M1: Authentication \& Verification Module
  \item M2: User Profile Module
  \item M3: Route \& Trip Module
  \item M4: Matching Module
  \item M5: Scheduling Module
  \item M6: Notification Module
  \item M7: Rating \& Feedback Module
  \item M8: Safety \& Reporting Module
  \item M9: Payment \& Cost Estimation Module
  \item M10: Admin \& Moderation Module
\end{itemize}

\item[\textbf{5.3 Software-Decision Modules}]  
These modules encapsulate internal logic, algorithms,  
and implementation decisions not visible to users.

\begin{itemize}
  \item M11: Pricing Module
  \item M12: Database Module
\end{itemize}

\end{description}

\begin{table}[h!]
\centering
\begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Level 1} & \textbf{Level 2}\\
\midrule
Hardware-Hiding Module & None\\
\midrule
\multirow{10}{0.3\textwidth}{Behaviour-Hiding Module}
& M1: Authentication \& Verification Module\\
& M2: User Profile Module\\
& M3: Route \& Trip Module\\
& M4: Matching Module\\
& M5: Scheduling Module\\
& M6: Notification Module\\
& M7: Rating \& Feedback Module\\
& M8: Safety \& Reporting Module\\
& M9: Payment \& Cost Estimation Module\\
& M10: Admin \& Moderation Module\\
\midrule
\multirow{2}{0.3\textwidth}{Software-Decision Module}
& M11: Pricing Module\\
& M12: Database Module\\
\bottomrule
\end{tabular}
\caption{Module Hierarchy}
\label{TblMH}
\end{table}