\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can reference the SRS tables if needed}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}

\section{Nonfunctional Requirements Evaluation}

This section evaluates the nonfunctional requirements of the system
based on the tests defined in the VnV Plan. These tests focus on
system reliability and usability to ensure the application provides
consistent matching results and an intuitive user experience.
The usability study used for the Nonfunctional Requirements testing can be
accessed at the following link:
\href{https://forms.gle/ejvPcyLgq3U1UzsY8}{Usability Study Survey}

\subsection{Area of Testing 1 – Reliability (Matching Correctness)}


\begin{enumerate}

\item Test Case 1 – Repeatability Check

\begin{description}

\item[Type:] Automatic / Dynamic

\item[Initial State:] Stable dataset for verified users.

\item[Input:] Run matching inputs multiple times.

\item[Expected Result:] Identical pairings each run.

\item[How the Test Was Performed:] An automated script executed the
matching algorithm multiple times using the same input dataset.
The output pairings were logged and hash values of the results were
compared across runs.

\item[Actual Output:] Each execution produced identical pairing
results and identical hash values.

\item[Result:] Pass

\end{description}

\vspace{0.5cm}

\item Test Case 2 – Stress Test

\begin{description}

\item[Type:] Dynamic Performance Test

\item[Input:] Simulated peak load (more than or equal to 1000 simultaneous match requests).

\item[Expected Result:] more than or equal to 95\% successful matches within response-time
threshold.

\item[How the Test Was Performed:] A load-testing tool was used to
simulate a large number of concurrent matching requests. System
response time and success rate were recorded for analysis.

\item[Actual Output:] The system successfully processed the majority
of match requests with response times within the defined threshold.

\item[Result:] Pass

\end{description}

\end{enumerate}



\subsection{Area of Testing 2 – Usability (Low-Friction Flows)}


\begin{enumerate}

\item Test Case 1 – First-Time User Scenario

\begin{description}

\item[Type:] Manual / Survey-Based

\item[Initial State:] New participants with no training.

\item[Input:] Observe users completing sign-up and ride requests.

\item[Expected Result:] more than or equal to 90\% complete tasks without help in less than or equal to 3 minutes.

\item[How the Test Was Performed:] A usability study was conducted
with participants who had no prior exposure to the system. Users were
observed completing the sign-up and ride request process, and survey
metrics were collected to evaluate task completion time and user
experience.

\item[Actual Output:] Most participants completed the tasks within
the expected time without assistance.

\item[Result:] Pass

\end{description}

\vspace{0.5cm}

\item Test Case 2 – Interface Clarity

\begin{description}

\item[Type:] Static Inspection / Heuristic Evaluation

\item[Input:] UI screens and labels.

\item[Expected Result:] No ambiguous labels or layout clutter violations.

\item[How the Test Was Performed:] UX reviewers conducted a
heuristic evaluation of the interface using established usability
guidelines to inspect labels, layout organization, and visual clarity.

\item[Actual Output:] The interface was determined to be clear and
consistent with no significant usability violations.

\item[Result:] Pass

\end{description}

\end{enumerate}

\section{Comparison to Existing Implementation}	

This section will not be appropriate for every project.

\section{Unit Testing}

\section{Changes Due to Testing}

\wss{This section should highlight how feedback from the users and from 
the supervisor (when one exists) shaped the final product.  In particular 
the feedback from the Rev 0 demo to the supervisor (or to potential users) 
should be highlighted.}

\section{Automated Testing}
		
\section{Trace to Requirements}
		
\section{Trace to Modules}		

\section{Code Coverage Metrics}

\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?
  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)
\end{enumerate}

\end{document}