\section{Methodology}
\label{sec:methodology}

\subsection{Study Design}

Evaluation followed the \textbf{task scenarios} in Section~\ref{sec:task_scenarios} using \textbf{moderated, think-aloud style walkthroughs}. Due to course timeline constraints, sessions used \textbf{simulated personas} (team-assigned roles and scripted reactions) rather than external recruitment. Section~\ref{sec:results} reports \textbf{illustrative aggregates} ($N=10$) consistent with those walkthroughs; they demonstrate the reporting format and plausible friction points but \textbf{do not constitute a live human-subjects study} or statistically validated benchmark.

\subsection{Participants}

\begin{itemize}
  \item \textbf{Simulated sample:} $N=10$ notional participants (personas P1--P10), each mapped to rider- or driver-oriented task subsets as in Section~\ref{sec:results}.
  \item \textbf{Role mix:} Six sessions emphasized \textbf{rider} tasks (UT-2), four emphasized \textbf{driver} tasks (UT-3); all personas walked through UT-1, UT-4, and UT-5 where applicable.
  \item \textbf{Scope:} \textbf{UT-2R} (recurring rides) was \textbf{out of scope} for this evaluation; drivers used \textbf{ONE-TIME} only in UT-3.
\end{itemize}

\subsection{Environment and Materials}

\begin{itemize}
  \item \textbf{Devices:} Two \textbf{Android} phones running the Hitchly Expo client against the same backend.
  \item \textbf{API and database:} Application traffic went to the \textbf{Render}-hosted API; persistent data used \textbf{Neon} (PostgreSQL).
  \item \textbf{Network:} Stable Wi-Fi; same \texttt{EXPO\_PUBLIC\_API\_URL} for both devices (see \path{apps/mobile/lib/trpc.ts}).
  \item \textbf{State reset between scenarios/personas:} Test \textbf{accounts were deleted} and flows restarted \textbf{from fresh registration} so trips, requests, and matches did not carry over spuriously.
  \item \textbf{Ethics note:} No external participants were recorded; simulated quotes in Section~\ref{sec:results} are \textbf{paraphrased narrative examples} from team walkthroughs, not verbatim recordings.
\end{itemize}

\subsubsection{Trip flows (configuration used)}

\noindent\textbf{Recurring rides (UT-2R):} Not evaluated; documented only for future reference in Section~\ref{sec:task_scenarios}.

\noindent\textbf{Accounts:} New \texttt{@mcmaster.ca} test accounts created per reset; email verification exercised as in UT-1; home address set before UT-2/UT-3 when testing posting or search.

\subsection{Session Outline}

\begin{enumerate}
  \item Briefing and simulated consent script (Appendix~\ref{sec:appendix}).
  \item Optional background questionnaire (not all personas recorded).
  \item Fixed order: UT-1 $\rightarrow$ UT-2 or UT-3 (by persona) $\rightarrow$ UT-4 $\rightarrow$ UT-5.
  \item Post-task prompts from Section~\ref{sec:questions_surveys} (ease rating captured per task).
  \item SUS-style ratings assigned per persona for aggregation (Appendix~\ref{sec:appendix}).
  \item Team debrief and log update before account deletion / next persona.
\end{enumerate}

\subsection{Data Recording}

For each task, record: start/end time, success or failure, number and type of assists (minimal prompt vs.\ direct help), and brief qualitative notes (quotes, confusion points). Use a session log template (spreadsheet or form) referenced in Section~\ref{sec:results}.
