\section{Task Scenarios}
\label{sec:task_scenarios}

Each scenario supports the goals in Section~\ref{sec:goals} and traces to the functional evaluation areas in the Verification and Validation report (\texttt{docs/VnVReport}). Navigation details match the Expo app in \texttt{apps/mobile} as of this document. Success criteria are \textbf{binary} unless noted. \textbf{UT-2R} (recurring rides) was not part of this study; drivers used one-time rides only in UT-3.

\subsection{Mapping to VnV functional areas}

Table~\ref{tab:vnv_ut_map} links each task to the VnV report areas (admin-only checks, such as reports in an admin dashboard, are out of scope for end-user tasks).

\begin{table}[htbp]
  \centering
  \caption{Task scenarios mapped to VnV functional evaluation areas.}
  \label{tab:vnv_ut_map}
  \begin{tabularx}{\textwidth}{l l X}
    \toprule
    \textbf{VnV area} & \textbf{Task ID(s)} & \textbf{Covered in usability testing}\\
    \midrule
    1 -- User verification & UT-1 & Sign-up, email verification, and clear handling of invalid or incomplete inputs.\\
    2 -- User profile & UT-5 & Updating profile fields; address and role as needed for other tasks.\\
    3 -- Ride matching & UT-2, UT-3, UT-4 & Search and proposals; posting a ride; accept, decline, no match, or blocked states.\\
    4 -- Cost estimation & UT-2, UT-4 & Reading the estimated share on a match card; optional moderator-prepared state if pricing updates when another rider joins.\\
    5 -- Review and reporting & UT-6, UT-7 & Submitting a rating after a trip; submitting a report through the in-app safety flow.\\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Scenario UT-1: Sign-up, verification, and input errors (Area 1)}

\textbf{Part A --- successful path}

\begin{itemize}
  \item \textbf{Context:} New McMaster student; Hitchly just installed.
  \item \textbf{Task:} Create an account with a McMaster-affiliated email, complete verification as required, and reach the main screen after sign-in.
  \item \textbf{Success:} Account created; verification step completed (or correctly attempted for the test account); participant reaches the post-auth home with at most one standard hint from the moderator.
\end{itemize}

\textbf{Part B --- invalid or incomplete inputs}

\begin{itemize}
  \item \textbf{Task:} With moderator guidance, try at least one invalid case: wrong email format, password below the app's rules, or (for driver test accounts) attempting driver registration without a required license upload if the flow asks for it. Correct inputs until errors clear or the participant explains the message.
  \item \textbf{Success:} The app shows understandable errors for bad input; the participant recovers without repeated moderator help beyond one hint. Judge clarity and recovery, not server-side test-case IDs.
\end{itemize}

\subsection{Scenario UT-2: Rider --- search, cost, pass, and request (Areas 3 and 4)}

\textbf{Prerequisite:} Home address on profile. If missing, the app prompts to open profile; moderator confirms a seeded account or allows a short address sub-task.

\begin{itemize}
  \item \textbf{Start:} Rider home; open find-a-ride if needed (e.g.\ from ``My Rides'').
  \item \textbf{Task:}
  \begin{enumerate}
    \item Set route direction (to or from McMaster), date, and arrival time per moderator script.
    \item If travelling to campus, pick the moderator's drop-off from the campus list.
    \item Run search and wait until results load.
    \item On at least one match card, find and say aloud the \textbf{estimated cost} (dollar amount).
    \item If two or more cards appear: swipe left on one card to pass, then swipe right on another to request. If only one card: swipe left to pass, then use new search or note empty deck per script.
    \item If there are no matches, read the empty state (e.g.\ no matches found) and optionally start a new search.
    \item Optional: open trip details from a card tap.
  \end{enumerate}
  \item \textbf{Success:} Search runs from a valid form; participant reaches a swipe deck, trip details, or the no-match state without stuck validation; they correctly describe swipe-right as requesting a ride and report the cost they saw (or honestly say no cost was visible).
  \item \textbf{Cost update (Area 4, optional):} If the moderator prepared a ride where the estimate changes after another rider joins, ask the participant to compare before and after. Otherwise only the on-card estimate in this task is required.
\end{itemize}

\subsection{Scenario UT-2R: Recurring ride (reference only)}

\textbf{Not in scope.} Documented for future runs. In this study, drivers chose a one-time ride in UT-3.

\begin{itemize}
  \item \textbf{Driver (future):} Post Ride $\rightarrow$ recurring $\rightarrow$ set direction, departure, seats $\rightarrow$ publish.
  \item \textbf{Rider (future):} From My Rides on a recurring booking, use request-next when shown.
\end{itemize}

\subsection{Scenario UT-3: Driver --- post a ride (Area 3)}

\begin{itemize}
  \item \textbf{Start:} Driver trips list; open Post Ride (post-a-ride modal).
  \item \textbf{Prerequisite:} Home address on profile; moderator uses a seeded account or allows profile setup time.
  \item \textbf{Task:} Choose direction (to or from McMaster); keep repeat on \textbf{one-time}; set departure and seats; publish.
  \item \textbf{Success:} Publish completes (modal closes or trip appears in the list) without blocking errors, or the participant gets a clear error that the moderator logs as a defect.
\end{itemize}

\subsection{Scenario UT-4: Accept, decline, or blocked match (Area 3; Area 4 if cost shown)}

Moderator sets state so the participant has a pending match, request, or trip action.

\begin{itemize}
  \item \textbf{Rider path (examples):} Confirm or cancel a request; open a matched trip; respond to prompts that accept or end the match. If the UI shows a cost or status change, note whether it is clear.
  \item \textbf{Driver path (examples):} Open pending requests for a trip; \textbf{accept} one rider or \textbf{reject} one when the script asks; confirm the UI reflects the choice (e.g.\ confirmed vs.\ rejected).
  \item \textbf{No match / blocked:} If the script uses a dead-end state, success is correctly describing the message and next step.
  \item \textbf{Success:} The participant reaches the intended state (accepted, declined, cancelled, or no match) or clearly explains why the screen blocked them; moderator notes any ambiguity.
\end{itemize}

\subsection{Scenario UT-5: Profile update (Area 2)}

\begin{itemize}
  \item \textbf{Task:} Change a non-sensitive field (for example phone or display name) and save. If time allows, locate notification or payment-related settings and report whether they exist and where.
  \item \textbf{Success:} Update saves as expected, or failure is documented; settings located within the time threshold in Section~\ref{sec:metrics} or participant explains why they stopped.
\end{itemize}

\subsection{Scenario UT-6: Review after a trip (Area 5)}

\begin{itemize}
  \item \textbf{Prerequisite:} Moderator places the account on a completed or review-eligible trip (same build as production test data).
  \item \textbf{Task:} Open the review flow for that trip, set rating(s), and submit.
  \item \textbf{Success:} Submission completes with success feedback (or the participant describes a blocking issue for the log).
\end{itemize}

\subsection{Scenario UT-7: Safety report (Area 5)}

\begin{itemize}
  \item \textbf{Prerequisite:} Active or completed trip context where Report is available (rider ride screen, driver drive screen, or trip details per moderator script).
  \item \textbf{Task:} Open Report (safety flow), complete the steps the moderator specifies for the test environment, and submit.
  \item \textbf{Success:} Report submits with confirmation, or the participant describes a clear blocker.
\end{itemize}

\begin{table}[htbp]
  \centering
  \caption{Task scenario summary (UT-2R not run; quantitative outcomes in Section~\ref{sec:results}).}
  \label{tab:task_summary}
  \begin{tabular}{lll}
    \toprule
    \textbf{ID} & \textbf{Focus} & \textbf{Notes}\\
    \midrule
    UT-1 & Verification and input errors & Areas 1\\
    UT-2 & Rider search, cost, pass/request & Areas 3, 4\\
    UT-2R & Recurring ride & Not in scope\\
    UT-3 & Driver post ride & Area 3\\
    UT-4 & Match accept / decline / blocked & Areas 3, 4\\
    UT-5 & Profile update & Area 2\\
    UT-6 & Post-trip review & Area 5\\
    UT-7 & In-app report & Area 5\\
    \bottomrule
  \end{tabular}
\end{table}
