\section{Session Questions and Survey Instruments}
\label{sec:questions_surveys}

\subsection{Pre-session Background Questions}

\begin{enumerate}[label=\textbf{Q\arabic*:}]
  \item How often do you commute to or from McMaster (or campus)?
  \item Do you usually drive, ride as a passenger, or use transit?
  \item Have you used any rideshare or carpool apps before? Which?
  \item What device are you using today?
\end{enumerate}

\subsection{Post-task Probing Questions}

After each scenario (Section~\ref{sec:task_scenarios}), ask as appropriate:

\begin{enumerate}[label=\textbf{PT\arabic*:}]
  \item What did you think that screen was asking you to do?
  \item Was anything surprising or unclear?
  \item On a scale of 1 (very difficult) to 7 (very easy), how easy was that task? (Record numeric response.)
  \item Did you feel you could trust the information the app showed (e.g., cost, other user, timing)?
\end{enumerate}

\subsection{Post-session Interview Questions}

\begin{enumerate}[label=\textbf{PS\arabic*:}]
  \item Overall, how would you describe your experience using Hitchly today?
  \item What would you change first if you could?
  \item Would you use this for real commuting if it were available? Why or why not?
  \item Any concerns about safety, privacy, or payments?
\end{enumerate}

\subsection{Standardized Questionnaires}

\begin{itemize}
  \item \textbf{System Usability Scale (SUS):} Administer the standard 10-item SUS immediately after tasks; compute the standard 0--100 score per participant. Full wording appears in Appendix~\ref{sec:appendix}.
  \item \textbf{Optional supplementary Likert blocks:} e.g., trust in campus verification, clarity of pricing---use 5- or 7-point scales with anchors ``Strongly disagree'' / ``Strongly agree''; include items in Appendix~\ref{sec:appendix}.
\end{itemize}

All numeric survey responses feed the quantitative analysis described in Section~\ref{sec:metrics}.
