\section{Metrics and Quantification}
\label{sec:metrics}

This section defines how usability is measured to satisfy \textbf{rigorous, quantified} reporting. Fill aggregate values in Section~\ref{sec:results} after data collection.

\subsection{Task Performance}

\begin{itemize}
  \item \textbf{Task success rate:} For each UT-$n$, proportion of participants who meet success criteria without failure. Report per-task and overall.
  \item \textbf{Time on task:} Elapsed time from moderator prompt to success or abandonment; report median, interquartile range, and outliers.
  \item \textbf{Assists:} Count moderator prompts (minimal hint vs.\ substantive help); define weighting if a composite ``error score'' is used.
  \item \textbf{Critical incidents:} Count usability problems by severity (blocks task / major / minor); use a simple rubric agreed before sessions.
\end{itemize}

\subsection{Subjective Measures}

\begin{itemize}
  \item \textbf{SUS score:} Per participant and mean $\pm$ standard deviation across $N$.
  \item \textbf{Post-task ease (1--7):} Mean per task from PT3 (Section~\ref{sec:questions_surveys}).
  \item \textbf{Optional Likert composites:} Mean scores per construct (e.g., trust, clarity).
\end{itemize}

\subsection{Analysis}

\begin{itemize}
  \item Summarize quantitative results in tables; use figures (e.g., bar chart of success rates) if required by the course.
  \item Thematic analysis on open-ended responses: tag recurring themes and link to screenshots or timestamps when recordings exist.
  \item Map top issues to SRS FR/NFR or design modules where applicable for traceability.
\end{itemize}

\subsection{Thresholds (optional targets)}

Document any targets set before testing (e.g., at least 80\% success on UT-1, median SUS $\geq$ 68). Revise after pilot if unrealistic for the current build.
