\newpage{}

\phantomsection
\label{sec:appendix}

\section*{Appendix --- Survey Instruments and Consent}

\subsection*{Consent Script (Outline)}

\begin{itemize}
  \item Purpose of the session; voluntary participation; right to stop.
  \item Recording (screen/audio) if used; storage and who may view data.
  \item No penalty for withdrawal; approximate duration.
  \item Contact for questions.
\end{itemize}

\subsection*{System Usability Scale (SUS)}

For each item, use a 5-point scale from \textbf{Strongly disagree} (1) to \textbf{Strongly agree} (5). Score using the standard SUS formula (odd items: score $= $ response $- 1$; even items: score $= 5 - $ response; sum $\times 2.5$ for 0--100).

\begin{enumerate}
  \item I think that I would like to use this system frequently.
  \item I found the system unnecessarily complex.
  \item I thought the system was easy to use.
  \item I think that I would need the support of a technical person to be able to use this system.
  \item I found the various functions in this system were well integrated.
  \item I thought there was too much inconsistency in this system.
  \item I would imagine that most people would learn to use this system very quickly.
  \item I found the system very cumbersome to use.
  \item I felt very confident using the system.
  \item I needed to learn a lot of things before I could get going with this system.
\end{enumerate}

\subsection*{Optional Likert Items (Trust and Clarity)}

Use 7-point Likert scales (1 = Strongly disagree, 7 = Strongly agree).

\begin{enumerate}
  \item I trust that other users on this app are affiliated with McMaster as claimed.
  \item The app's pricing or cost information was clear.
  \item I understood what would happen after I confirmed a ride or match.
  \item I felt my personal information was handled appropriately for a student project prototype.
\end{enumerate}

\subsection*{Session Log Template (Fields)}

\begin{itemize}
  \item Participant ID (anonymous); date; moderator; device/OS; build.
  \item Per task (UT-1 through UT-7 as applicable): start time, end time, success Y/N, assists, notes.
  \item SUS total; optional Likert means.
\end{itemize}
