\section{Admin/Moderation Module}

\subsection{Module}
This module handles the distribution of user roles and management of admin controls. This also controls and monitors activity and ensures strict policy enforcement.

\paragraph{Frontend}
This layer is responsible for providing an admin dashboard with flagged content, user complaints, user roles, and application analytics. 

\paragraph{Backend}
This layer is responsible for handling communication with RESTAPI endpoints using AdminRouter to manage user accounts and rides. Additionally, it runs the logic for handling role-based authentication. 

\paragraph{Data}
\begin{itemize}
    \item \textbf{Admin Table:} This would include profile information about admin.
    \item \textbf{Ride Table:} This would include information about users with warnings/bans.
    \item \textbf{User Analytics Table:} This includes a dataset of user and application statistics.
\end{itemize}

\subsection{Uses}
\begin{itemize}
    \item \textbf{Database Module:} This is used to retrieve and store pricing details.
    \item \textbf{Authentication \& Verification Module:} This is used to manage admin login and permissions.
\end{itemize}

\subsection{Syntax}

\paragraph{Exported Constants}
\begin{itemize} 
    \item \texttt{warning\_threshold= 3}  
    Maximum warnings before putting an account ban.
\end{itemize}

\paragraph{Exported Access Programs}
\par\vspace{0.5em}

\begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{l l l l}
\toprule
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\midrule
\texttt{warn\_user()} & user\_ID, reason & Bool (check if user is successfully warned) & NotFoundError, InsufficientAdminPrivileges \\
\texttt{get\_Reports()} & None & Returns a dataset of user reports & NotFoundError, InsufficientAdminPrivileges \\
\texttt{get\_analytics()} & None & Returns a dataset of user and application statistics & NotFoundError, InsufficientAdminPrivileges \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection{Semantics}

\paragraph{State Variables}
N/A

\paragraph{Environment Variables}
\begin{itemize}
    \item Secure HTTPS connection to API.
    \item Secure API connection for stable admin controls and management.  
\end{itemize}

\paragraph{Assumptions}
\begin{itemize}
    \item All admin permissions function properly. 
    \item All database services are full functional and stable.
    \item All API connections are functional and stable.
\end{itemize}


\paragraph{Access Routine Semantics}

\texttt{warn\_user()}:
\begin{itemize}
    \item \textbf{transition:} Adds a new record with a warning in the reports table.
    \item \textbf{output:} Bool (check if user is successfully warned).
    \item \textbf{exception:} NotFoundError (user\_ID not found), InsufficientAdminPrivileges.
\end{itemize}

\texttt{get\_Reports()}:
\begin{itemize}
    \item \textbf{transition:} None.
    \item \textbf{output:} Returns a dataset of user reports.
    \item \textbf{exception:} NotFoundError (empty dataset), InsufficientAdminPrivileges.
\end{itemize}

\texttt{get\_analytics()}:
\begin{itemize}
    \item \textbf{transition:} None.
    \item \textbf{output:} Returns a dataset of user and application statistics.
    \item \textbf{exception:} NotFoundError (empty dataset), InsufficientAdminPrivileges.
\end{itemize}


\paragraph{Local Functions}
\begin{itemize}
    \item \texttt{check\_privilege(admin\_ID, endpoint): bool} --- This function validates admin privileges and returns a bool to indicate whether they have sufficient privileges or not.
\end{itemize}

%-------------------